The Influence of Radial Drift and Gas Accretion on the C/O Ratio in Protoplanetary Disks

### 2016-04-14 Dissertate-Harvard-LaTeX/chapters/chapter1.tex
upd

Dynamical models are needed to understand how runaway growth ends and final planet masses are determined.  Relevant processes -- including gap opening in disks and the transition of accretion from spherical to planar -- can be simulated and then added to atmospheric evolution calculations \citep{LisHub09}.

@@

Aside from this insight, the analytic model is useful because, despite the amplitude error, it explains the basic scaling of numerical cooling models.  As is well known \citep{HubBod05}, a lower opacity, here scaling with $F_\kappa$, allows faster cooling and gives a lower critical core mass.  The cooling timescale and critical core mass depend only weakly on the disk pressure, via the logarithmic factor $\xi$.   The almost exponential rise in radiative zone pressure with depth, see \Eq{eq:PcbRcb}, explains why disk pressure has only a weak effect on cooling at the RCB.  %AY: add density explanation?

@@

In \Fig{fig:LtvsMopacity}, our standard dust opacity, \Eq{eq:opacitylaw}, is reduced by factors of 10 and 100.  Lower opacities result in higher luminosities and faster evolution.  Our model thus confirms a well-established result \citep{HubBod05}.  While clearly an important effect, atmospheric dust opacities are difficult to robustly predict. Ablation of infalling solids is a dust source.  Sinks include the sequestration of solids in the core and dust settling through the radiative zone.  Grain growth both reduces dust opacities per unit mass and favors settling.  Our scenario of negligible ongoing particle accretion tends to favor low dust opacities.   To be conservative, however, our reference case considers full Solar abundances. The effect of opacity reduction on the critical core mass is described in \S\ref{sec:critical}.

@@

\item A larger mean molecular weight reduces critical core masses, in agreement with \citet{HorIko11}.  If enrichment in heavy elements correlates with increased dust opacity, then the stronger opacity effect will dominate, increasing $\MC$.

>>>>

Dynamical models are needed to understand how runaway growth ends and final planet masses are determined.  Relevant processes -- including gap opening in disks and the transition of accretion from spherical to planar -- can be simulated and then added to atmospheric evolution calculations \citep{lissauer09}.

@@

Aside from this insight, the analytic model is useful because, despite the amplitude error, it explains the basic scaling of numerical cooling models.  As is well known \citep{hubickyj05}, a lower opacity, here scaling with $F_\kappa$, allows faster cooling and gives a lower critical core mass.  The cooling timescale and critical core mass depend only weakly on the disk pressure, via the logarithmic factor $\xi$.   The almost exponential rise in radiative zone pressure with depth, see \Eq{eq:PcbRcb}, explains why disk pressure has only a weak effect on cooling at the RCB.  %AY: add density explanation?

@@

In \Fig{fig:LtvsMopacity}, our standard dust opacity, \Eq{eq:opacitylaw}, is reduced by factors of 10 and 100.  Lower opacities result in higher luminosities and faster evolution.  Our model thus confirms a well-established result \citep{hubickyj05}.  While clearly an important effect, atmospheric dust opacities are difficult to robustly predict. Ablation of infalling solids is a dust source.  Sinks include the sequestration of solids in the core and dust settling through the radiative zone.  Grain growth both reduces dust opacities per unit mass and favors settling.  Our scenario of negligible ongoing particle accretion tends to favor low dust opacities.   To be conservative, however, our reference case considers full Solar abundances. The effect of opacity reduction on the critical core mass is described in \S\ref{sec:critical}.

@@

\item A larger mean molecular weight reduces critical core masses, in agreement with \citet{hori11}.  If enrichment in heavy elements correlates with increased dust opacity, then the stronger opacity effect will dominate, increasing $\MC$.
